---
title: "Similarity of African Countries Development over Time"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r}

library(dplyr) 
library(tmap) # for mapping
library(fields) # a faster way to compute dist matrixes, output is matrix, not 'dist'
library(reshape) # necessary to transform distance matrix into long format
library(sf) # needed to code dataframes into 'sf' format (st_as_st)
library(shiny) # 
library(leaflet)

setwd("C:\\Users\\rsolt008\\Documents\\personal git\\WorldBank Shiny App\\Dashboard/") 
load("C:\\Users\\rsolt008\\Documents\\personal git\\WorldBank Shiny App\\NN_dataset.rdata")
#load("C:\\Users\\rsolt008\\Documents\\personal git\\WorldBank Shiny App\\worldBank_raw_wide.rdata")
load("C:\\Users\\rsolt008\\Documents\\personal git\\WorldBank Shiny App\\dat_wide.rdata")


bins <- c(0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, Inf)
pal <- colorBin("YlOrRd", domain = nn_dist_viz$Distance, bins = bins,reverse = T)


nn_dist_viz <- dplyr::left_join(nn_dist_viz,dat_wide, 
                                by=c("Country_Comp"="country","Year"="year"))

# nn_dist_viz is 88 mb large

clist<-unique(nn_dist_viz$Country_Focus)

```



Nearest Neigbors
=====================================     

Column {data-width=400, .sidebar}
-------------------------------------
### Select Country and Year 
      
```{r}

selectInput("Variable", "Country:",
                choices = clist)
    
sliderInput("Year",
                "Year:",
                min = 1991,
                max = 2016,
                value= 1991,
                step= 1,
                sep = "")

# Reactive expression for the given country in the Title
  formulaText <- reactive({
    paste("Similarity Mapping for", input$Variable)
  })
  
  # Return the formula text for printing as a caption
  output$caption <- renderText({
    formulaText()
  })
  
  #############
  
  # Reactive expression for the given country dataset
  nn_dist_sub <- reactive({
    tmp_dist <- nn_dist_viz[ which ( nn_dist_viz$Country_Focus==input$Variable & nn_dist_viz$Year==input$Year ) , ]
    tmp_dist 
    
    })
  
  
  nn_focus_country <- reactive({
    tmp_foc <- nn_dist_viz[ which (nn_dist_viz$Country_Comp==input$Variable & nn_dist_viz$Year==input$Year), ] 
    tmp_foc
    
  })

```
    
    
    
The selected country appears in blue on the map. All other African countries are colored a shade of yellow, orange, or red that relates to how similar their reported WBI (World Bank Indicators) were to the selected country for the given year.

Territories or countries that appear grey are missing data. Notable exclusions include South Sudan and the Eastern Western Sahara.


Column {data-width=600}
-------------------------------------

### "Nearest-Neighbors" Map 

```{r}
renderLeaflet({
    leaflet() %>%
      addTiles() %>%
      addPolygons(data=nn_dist_sub(),  
                  fillColor = ~pal(Distance), 
                  stroke = FALSE,
                  popup=paste("<b>","Country","</b>", nn_dist_sub()$Country_Comp, "<br>",
                              "GDP PPP:", nn_dist_sub()$GDP_pC_PPP, "<br>",
                              "Birth Rate:", nn_dist_sub()$birth_rate_per_K, "<br>",
                              "Electricity:", nn_dist_sub()$access_to_electricity_perc, "<br>",
                              "Unemployed:", nn_dist_sub()$Unemployment_perc),
                  popupOptions = popupOptions(maxWidth ="100%", 
                                              closeOnClick = TRUE)) %>%
      addPolygons(data=nn_focus_country(), 
                  fillColor = "#a6bddb",  
                  weight = 1,
                  opacity = 1,
                  color = "white",
                  dashArray = "3",
                  fillOpacity = .1) %>%
      addLegend(pal=pal, values=nn_dist_sub()$Distance, opacity = 0.7, title = "Similarity",
                position = "bottomright") 
  })

```



Time-Series Clusters
===================================== 

Column {data-width=400}
-------------------------------------

### Number of Clusters
    
```{r}
```
    
### Notes

These clusters are based upon .... 

Column {data-width=600}
-------------------------------------

### Results


Raw Data
===================================== 
    


### Raw Data
    
```{r}
setwd("C:\\Users\\rsolt008\\Documents\\personal git\\WorldBank Shiny App\\")
load("worldBank_raw_wide.rdata")

library(DT)
DT::datatable(worldBank_raw_wide, options = list(
  bPaginate = TRUE
))

```
    

### Notes

All metrics reported are standard World Bank Indicators (WBI) which were collected from African regions and countries from 2001-2016. Not all records are complete, with notable ommissions for Central African Republic, Mauritania, Southern Sudan, and the Western Sahara.

**GDP_pC_PPP** - GDP per capita, PPP (current international $) - NY.GDP.PCAP.PP.CD  
**birth_rate_per_K** - Birth rate, crude (per 1,000 people) - SP.DYN.CBRT.IN  
**access_to_electricity_perc** - Access to electricity (% of population) - EG.ELC.ACCS.ZS  
**Unemployment_perc** - Unemployment, total (% of total labor force) (modeled ILO estimate) - SL.UEM.TOTL.ZS  


